Iterative Unfolding Optimization with the Mean Squared Error Metric

### 2019-10-10 NOvA/numu/mean_squared_error_metric/mse_metric.tex
Adding cartoons.

>>>>

%================================================================================
\begin{frame}{Pseudo-experiments Generated}
  \begin{columns}
    \begin{column}{.5\textwidth}
      \includegraphics[width=\textwidth]{figures/pseudoexp_true.eps}
    \end{column}
    \begin{column}{.5\textwidth}
      \includegraphics[width=\textwidth]{figures/pseudoexp_reco.eps}
    \end{column}
  \end{columns}
\end{frame}

%================================================================================
\begin{frame}{Unfolded Spectra (Input, Standard Deviation as Error)}
  \centering
  \includegraphics[height=\textheight]{figures/unfolded_pseudo_exps_iter0.eps}
\end{frame}

%================================================================================
\begin{frame}{Unfolded Spectra 1 Iteration (Standard Deviation as Error)}
  \centering
  \includegraphics[height=\textheight]{figures/unfolded_pseudo_exps_iter1.eps}
\end{frame}

%================================================================================
\begin{frame}{Unfolded Spectra 2 Iteration (Standard Deviation as Error)}
  \centering
  \includegraphics[height=\textheight]{figures/unfolded_pseudo_exps_iter2.eps}
\end{frame}

%================================================================================
\begin{frame}{Unfolded Spectra 4 Iteration (Standard Deviation as Error)}
  \centering
  \includegraphics[height=\textheight]{figures/unfolded_pseudo_exps_iter4.eps}
\end{frame}

%================================================================================
\begin{frame}{Unfolded Spectra 6 Iteration (Standard Deviation as Error)}
  \centering
  \includegraphics[height=\textheight]{figures/unfolded_pseudo_exps_iter6.eps}
\end{frame}

%================================================================================
\begin{frame}{Unfolded Spectra 10 Iteration (Standard Deviation as Error)}
  \centering
  \includegraphics[height=\textheight]{figures/unfolded_pseudo_exps_iter10.eps}
\end{frame}

%================================================================================
\begin{frame}{Unfolded Spectra 100 Iteration (Standard Deviation as Error)}
  \centering
  \includegraphics[height=\textheight]{figures/unfolded_pseudo_exps_iter100.eps}
\end{frame}
